Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd
update to do list
corrects lift and confidence for app

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
   AR_expanded_taken, AR_expanded_PF, AR_expanded_HL, AR_expanded_Grade)
```

### CSPADE Algorithm
##TODO: add AR_grade, SR_grade

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    rename(confidence.old = "confidence", lift.old="lift")%>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = support / lhs.rhsCourse.support,
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students

      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support

@@

    SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL, SR_expanded_Grade)

>>>>

```
We save and remove objects:
```{r saving and rm}
#
# Save association rules
save(AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
     AR_expanded_taken, 
     #AR_expanded_PF, AR_expanded_HL, 
     AR_expanded_Grade,
     file = "App/AR.RDATA")

# Remove objects
rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_Grade, 
   AR_expanded_taken, 
   #AR_expanded_PF, AR_expanded_HL, 
   AR_expanded_Grade)
```

### CSPADE Algorithm
##TODO: fine tune parameters of cspade and ruleInduction, not taken --> fail,

@@

  rules %>%
    as("data.frame") %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]"),
      rule = str_remove_all(rule, pattern = "[{]"),
      rule = str_remove_all(rule, pattern = "[}]"),
      rule = str_remove_all(rule, pattern = "[>]")
      ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=")  %>%
    select(
      lhs, rhs,
      support,
      confidence,
      lift
    ) %>%
    separate(lhs, into=c("LHS Course ID", "LHS Quality"), sep="_", remove= F) %>%
    separate(rhs, into=c("RHS Course ID", "RHS Quality"), sep="_", remove= F) %>%
    # Compute statistic
    group_by(lhs,`RHS Course ID`) %>%
    mutate(
      lhs.rhsCourse.support = sum(support),
      confidence = support / lhs.rhsCourse.support,
      count = support * n_students,
      lhs.rhsCourse.count = lhs.rhsCourse.support * n_students,
      lift = NA
      # TODO: compute rhs.support
      # lift = confidence.corr / rhs.support

@@

    SR_expanded_taken, 
    #SR_expanded_PF, SR_expanded_HL, 
    SR_expanded_Grade,

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, 
   #sequences_expanded_PF, sequences_expanded_HL, 
   sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL, SR_Grade,
   SR_expanded_taken, 
  # SR_expanded_PF, SR_expanded_HL, 
   SR_expanded_Grade)
